\documentclass{article}
\usepackage[cm]{fullpage}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontspec}
\usepackage{array} 
\usepackage{booktabs, makecell, tabularx}
\usepackage{fontawesome}

\setmainfont{Corbel}

\hypersetup{breaklinks=true,%
pagecolor=white,%
colorlinks=true,%
linkcolor=cyan,%
urlcolor=MyDarkBlue}

\definecolor{MyDarkBlue}{rgb}{0,0.0,0.45}

%%%%%%%%%%%%%%%%%%%%%%%%%%
% Formatting parameters  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newlength{\tabin}
\setlength{\tabin}{1em}
\newlength{\secsep}
\setlength{\secsep}{0.mm}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\definecolor{contactgray}{gray}{0.3}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Template Definitions  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-6pt} \hrulefill \\ \vspace*{-15pt}}
\newcommand{\name}[1]{\begin{center}\textsc{\Huge#1}\\\end{center}}
\newcommand{\program}[1]{\begin{center}\color{teal}\textsc{#1}\end{center}}
\newcommand{\contact}[1]{\begin{center}\color{contactgray}{\small#1}\end{center}}

\newenvironment{tabbedsection}[1]{
  \begin{list}{}{
      \setlength{\itemsep}{0pt}
      \setlength{\labelsep}{0pt}
      \setlength{\labelwidth}{0pt}
      \setlength{\leftmargin}{\tabin}
      \setlength{\rightmargin}{\tabin}
      \setlength{\listparindent}{0pt}
      \setlength{\parsep}{0pt}
      \setlength{\parskip}{0pt}
      \setlength{\partopsep}{0pt}
      \setlength{\topsep}{#1}
    }
  \item[]
}{\end{list}}

\newenvironment{nospacetabbing}{
    \begin{tabbing}
}{\end{tabbing}\vspace{-1.2em}}

\newenvironment{resume_header}{}{\vspace{0pt}}
\newenvironment{resume_title}{}{\vspace{0pt}}

\newenvironment{resume_subsection}[2][]{
  \textbf{#2} \hfill {\footnotesize #1} \hspace{2em}
  \begin{tabbedsection}{0.5\secsep}
}{\end{tabbedsection}}

\newenvironment{subitems}{
  \renewcommand{\labelitemi}{-}
  \begin{itemize}
      \setlength{\small\labelsep}{1em}
}{\end{itemize}}

\newenvironment{resume_employer}[4]{
  \vspace{\secsep}
  \large\textbf{#1} \\
  \indent {\small #2} \hfill {\footnotesize#3 (#4)}
  \begin{tabbedsection}{0pt}
  \begin{subitems}
}{\end{subitems}\end{tabbedsection}}

\newenvironment{resume_section}[1]{
    \textbf{\Large\ruleline{\color{teal}{#1}}}
  \begin{tabbedsection}{\secsep}
}{\end{tabbedsection}}

\newcolumntype{b}{X}
\newcolumntype{s}{>{\hsize=.13\hsize}X}

\newcommand*\ruleline[1]{\par\noindent\raisebox{0ex}{\makebox[\linewidth]{{#1}\hspace{1ex}\hrulefill}}}


\begin{document}

\begin{resume_header}
    \name{Deni Arianto}
      \begin{resume_title}
      \color{blue}
        \program{Software Engineer $\bullet$ Computer Science Major $\bullet$ Mercu Buana University}
      \end{resume_title}
    \contact{ \faEnvelope \hspace{0.2} deni.arianto1606@gmail.com \hspace{0.2cm} | \hspace{0.2cm} \faMobilePhone \hspace{0.2} 08222-7777-936 \hspace{0.2cm} | \hspace{0.2cm} \faLinkedinSquare \hspace{0.2} https://www.linkedin.com/in/deniar16/ } 
    \end{resume_header}

\begin{resume_section}{About Me}
  \begin{table}[htbp]
      \centering
      \begin{tabularx}{\textwidth}{>{\raggedleft\arraybackslash}sb}
          \textbf{Programming}    & \hspace{0.5cm}\small Java, Python (Basic), Go (Basic), \LaTeX  \\ 
          \textbf{Database}       & \hspace{0.5cm}\small MySQL, PostgreSQL, MongoDB, Apache Cassandra \\ 
          \textbf{Messaging}      & \hspace{0.5cm}\small Apache Kafka, RabbitMQ \\ 
          \textbf{Web/Media}      & \hspace{0.5cm}\small HTML, CSS, Javascript\\ 
          \textbf{Languages}      & \hspace{0.5cm}\small Fluent in English; Conversational Proficiency in Indonesian \\ 
      \end{tabularx}
  \end{table}
\end{resume_section}

\begin{resume_section}{Experience}
    \begin{resume_employer}{tiket.com}
        {Flight Ancillary Team}{Jakarta, Indonesia}{August 2020-now}
        \item Define features along with Product Team and QA Team.
        \item Implement Multi Insurance Features.
        \item Refactor monolith insurance to reactive insurance using Java reactive stack.
        \item Refactor cart features to standalone Ancillary service (Baggage, Meal, Seat).
        \item Technology Research and Development. \\
      \end{resume_employer}
      \begin{resume_employer}{tiket.com}
        {Car Team}{Jakarta, Indonesia}{January 2019-August 2020}
        \item Define features along with Product Team and QA Team.
        \item Implement Car Features.
        \item Refactor monolith car to reactive insurance using Java reactive stack.
        \item Technology Research and Development. \\
      \end{resume_employer}
      \begin{resume_employer}{tiket.com}
        {Utilities Team}{Jakarta, Indonesia}{July 2018 - December 2018}
        \item Implement notification service for sending email using Java reactive stack. \\
      \end{resume_employer}
    
      \begin{resume_employer}{blanja.com}
        {Utilities Team}{Jakarta, Indonesia}{August 2017 - June 2018}
        \item Refactor email notification from monolith Dubbo framework.
        \item Implement voucher feature. \\
      \end{resume_employer}
\end{resume_section}

\begin{resume_section}{Awards and Honors}
    \begin{resume_subsection}[(2012)]{INAICTA (Ministry of Information and Communication of Republic Indonesia)}
    \begin{subitems}
      \item Nominee of Indonesia ICT Awards 2012 on Category Creative and Innovative New Media.
      \item Nominee of Indonesia ICT Awards 2012 on Category E-Government.
      \end{subitems}
    \end{resume_subsection}
\end{resume_section}
  
  
  \begin{resume_section}{Education}
    \begin{resume_subsection}[Jakarta, Indonesia (2014--2018)]{Mercu Buana University}
    \end{resume_subsection}
    
  \end{resume_section}

  
\end{document}